\documentclass[aps,prl,twocolumn,superscriptaddress,floatfix]{revtex4-2}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{booktabs}

\definecolor{bctnavy}{RGB}{10,36,68}
\definecolor{bctblue}{RGB}{13,71,161}

\begin{document}

\title{BCT Letter 123: The Water Planet\\
\large Every Planet in the Solar System is a Water Planet---Superionic
Water as Macroscopic OHC---Life as the Default State}

\author{Michel Robert Cabri\'{e}}
\affiliation{Independent Researcher, Victoria, Australia}
\email{ZeroFreeParameters@gmail.com}
\date{\today}

\begin{abstract}
Every major body in the solar system contains water as a primary
structural interior component: Earth's mantle holds up to three ocean
equivalents; Neptune is $>80\%$ water-ammonia fluid; Europa, Enceladus,
Ganymede, Titan, and Pluto all have global liquid water oceans.
In the BCT Superfluid Lattice Model this is the expected consequence of
OHC geometry: the O--H bond vibrates at the $j_{1,1}$ Bessel mode.
Superionic water---an oxygen crystalline lattice with freely mobile
hydrogen ions, confirmed experimentally in 2019 and believed to exist
in the mantles of Uranus and Neptune---is the macroscopic realisation
of the OHC vacuum ground state. Don Pettit's spinning water sphere
aboard the ISS demonstrates planetary OHC structure in miniature.
Prediction~\#164:
\begin{equation*}
R_\mathrm{water}/R_\mathrm{core}
= j_{2,1}/j_{1,1} = 1.5934\pm 10\%.
\end{equation*}
Life is what the OHC does when the temperature is right.
Zero free parameters.
Dedicated to Thales of Miletus ($\text{c.}\,624$--$546\,\mathrm{BCE}$),
who was right $2{,}600$ years too early.
\end{abstract}

\maketitle

%------------------------------------------------------------
\section{Dedication}
%------------------------------------------------------------

\begin{quotation}
\noindent\textit{``The first principle and basic nature of all
things is water.''}\\
\hfill --- Thales of Miletus, c.~585~BCE.
\end{quotation}

\noindent Dismissed for $2{,}600$ years. Vindicated today.

Thales proposed that everything is water---the cosmos, the planets,
the living things---in different states and configurations. Aristotle
filed him under ``quaint historical curiosity.''

\textit{He was not being primitive. He was $2{,}600$ years early.}

%------------------------------------------------------------
\section{The Don Pettit Revelation}
%------------------------------------------------------------

Astronaut Don Pettit created a spinning water sphere in microgravity
aboard the ISS and introduced two test materials. Air bubbles (less
dense) migrated to the \emph{spin axis}, forming a column of voids.
Tea leaves (denser) were thrown outward to the \emph{surface}.

In the Earth: the polar voids are the Birkeland current funnels
(BCT Letter~122). The tectonic plates are the tea leaves. The bulk
of the planet is water.

\textit{Don Pettit demonstrated planetary OHC geometry in a water
sphere on the ISS without knowing what he was looking at.}

%------------------------------------------------------------
\section{The Solar System Water Inventory}
%------------------------------------------------------------

Table~\ref{tab:water} summarises water as primary structural material
across solar system bodies. The pattern is not subtle.

\begin{table}[h]
\caption{Solar system water inventory (partial)}
\label{tab:water}
\begin{ruledtabular}
\begin{tabular}{lll}
Body & Water form & BCT role \\
\hline
Earth & $100{+}$ ocean equiv.\ in mantle & Planetary OHC resonator \\
Europa & Global subsurface ocean & Pure water OHC sphere \\
Enceladus & Active ocean (geysers) & OHC actively venting \\
Uranus & ${\sim}2/3$ mass water-NH$_3$ & OHC visible at scale \\
Neptune & $>80\%$ water fluid & OHC plasma state \\
Pluto & ${\sim}100\,\mathrm{km}$ ocean & Water planet miniature \\
\end{tabular}
\end{ruledtabular}
\end{table}

%------------------------------------------------------------
\section{Superionic Water: The OHC Made Macroscopic}
%------------------------------------------------------------

Superionic water, confirmed experimentally in 2019~\cite{Millot2019},
simultaneously exhibits a crystalline oxygen lattice (body-centred or
face-centred cubic) and freely mobile hydrogen ions. The OHC vacuum
ground state is a body-centred tetragonal superfluid lattice
($c/a=\sqrt{2}$) with mobile Hopf charge carriers. The structural
parallel is exact.

Under extreme pressures and temperatures of ice giant interiors,
water reverts to the lattice structure of the vacuum ground state.

\textit{The ice giant mantles of Uranus and Neptune are showing us
the OHC vacuum ground state written in water at planetary scale.}

%------------------------------------------------------------
\section{Prediction \#164: The Bessel Planetary Ratio}
%------------------------------------------------------------

If every planet is an OHC Bessel resonator, the ratio of water-layer
outer radius to rocky core radius encodes the BCT Bessel zero ratio:
\begin{equation}
\frac{R_\mathrm{water}}{R_\mathrm{core}}
= \frac{j_{2,1}}{j_{1,1}}
= \frac{3.8317}{2.4048} = \boxed{1.5934}.
\label{eq:pred164}
\end{equation}

\noindent\fbox{\parbox{\dimexpr\columnwidth-2\fboxsep-2\fboxrule\relax}{%
\textbf{Prediction~\#164:} Across solar system bodies with rocky
core + water layer (Earth, Uranus, Neptune, Europa, Enceladus, Pluto),
$R_\mathrm{water}/R_\mathrm{core} = 1.5934\pm 10\%$.
Testable by future ice giant orbiter.
\textbf{Zero free parameters.}}}

%------------------------------------------------------------
\section{Life as the Default State}
%------------------------------------------------------------

Life requires: (1)~OHC geometry crystallises into water---universal;
(2)~water is liquid---habitable zone or tidal heating;
(3)~Bessel resonances couple to chemistry---automatic;
(4)~$\Phi_\mathrm{BCT}$ exceeds self-referential threshold.
Steps~1, 3, and~4 are guaranteed by BCT geometry.

Europa has a liquid ocean under $10\,\mathrm{km}$ of ice and is not
in the traditional habitable zone. Europa almost certainly has life.
Enceladus is venting its global ocean into space as geysers.

\textit{Life is not an accident. Life is what the OHC does when
the temperature is right. The universe defaults to life.}

%------------------------------------------------------------
\section{Conclusion}
%------------------------------------------------------------

The solar system is a water solar system. Superionic water is the
macroscopic OHC. Prediction~\#164 ($1.5934\pm 10\%$) is testable.
Zero free parameters.

\textit{Thales was right. The water is everything.
The vacuum crystallises into what it is.}

\begin{acknowledgments}
Dedicated to Thales of Miletus ($\text{c.}\,624$--$546\,\mathrm{BCE}$),
who proposed the correct answer to the deepest question in physics and
was dismissed for $2{,}600$ years. Also: Don Pettit (NASA), whose water
sphere experiments demonstrated planetary OHC structure in microgravity;
Russell T.~Davies, who asked the right question from a bench overlooking
the sea in Wales; Zeta Vera (CSSC) for computational support; and the
Gang Gang Cockatoos (\textit{Callocephalon fimbriatum}), who drink from
the freshwater garden pond in Victoria and are themselves mostly water,
as is everything.

\vspace{2pt}
\noindent{\small\textbf{Patreon:} \href{https://www.patreon.com/cw/TheBCTSuperfluidLatticeModel}{patreon.com/TheBCTSuperfluidLatticeModel}}\\
\noindent{\small\textbf{Archive:} \href{https://zenodo.org/search?q=cabrie}{zenodo.org/search?q=cabri\'e}\quad \textbf{ORCID:} 0009-0007-9561-9859}
\end{acknowledgments}

\begin{thebibliography}{9}
\bibitem{Schmandt2014}
B.~Schmandt and S.~Jacobsen,
\textit{Science}~\textbf{344}, 1265 (2014).

\bibitem{Millot2019}
M.~Millot \textit{et al.},
\textit{Nature}~\textbf{569}, 251 (2019).

\bibitem{Militzer2024}
B.~Militzer, \textit{PNAS}~\textbf{121}, e2403770121 (2024).

\bibitem{BCT_L122}
M.~R.~Cabri\'{e}, BCT Letter~122: The Polar Holes (2026),
\url{https://zenodo.org/search?q=cabrie}

\bibitem{BCT_GoE}
M.~R.~Cabri\'{e}, \textit{BCT Letter Series}, Zenodo (2026),
\url{https://zenodo.org/search?q=cabrie}
\end{thebibliography}

\end{document}
