\documentclass[twocolumn,10pt,a4paper]{article}

\usepackage[margin=1.8cm,top=2cm,bottom=2cm]{geometry}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{hyperref}
\usepackage[dvipsnames]{xcolor}
\usepackage{booktabs}
\usepackage{array}
\usepackage{microtype}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{parskip}
\usepackage{enumitem}

\hypersetup{colorlinks=true,linkcolor=blue!60!black,citecolor=blue!60!black,urlcolor=blue!60!black}

\titleformat{\section}[block]{\normalsize\bfseries\centering}{}{0em}{}
\titleformat{\subsection}[runin]{\normalsize\itshape}{}{0em}{}[.\quad]
\titlespacing*{\section}{0pt}{10pt}{4pt}
\titlespacing*{\subsection}{0pt}{4pt}{0pt}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\textit{BCT Superfluid Lattice Model --- Letter 30}}
\fancyhead[R]{\small\textit{March 2026}}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

\setlength{\columnsep}{0.6cm}
\setlist[enumerate]{leftmargin=*,itemsep=2pt,topsep=2pt}
\setlist[itemize]{leftmargin=*,itemsep=2pt,topsep=2pt}

\begin{document}

\twocolumn[{%
\begin{center}
{\large\bfseries The Neutron--Proton Mass Difference at Sub-0.1\%:\\[2pt]
BCT Colour Casimir SU(6) Theorem}\\[8pt]
{\normalsize Michel Robert Cabri\'e$^{1,\ast}$}\\[4pt]
{\small $^1$Independent Researcher;\; ORCID: 0009-0007-9561-9859}\\[2pt]
{\small (Dated: March 2026)\quad BCT Letter 30}\\[10pt]
\end{center}
\begin{center}
\begin{minipage}{0.85\textwidth}
\small
We apply the BCT Colour Casimir Theorem established in Letter~29 to the
neutron--proton mass difference $\Delta m_N = m_n - m_p$.  At leading order,
the BCT SU(6) spin-flavour theorem gives
$\Delta m_N^{\rm LO} = \Lambda_{\rm QCD}\,\alpha_0\,\pi/4 = 1.280\,\mathrm{MeV}$
(Phase~48B, $-1.03\%$).  Applying the NLO Casimir correction
$F_{\rm SU(6)} \to F_{\rm SU(6)}\,(1 + C_F\alpha_0)$ with
$C_F = (N_c^2-1)/(2N_c) = 4/3$ yields
\[
  \Delta m_N = \frac{\Lambda\alpha_0\pi}{4}\,(1+C_F\alpha_0)
             = 1.2927\,\mathrm{MeV}\,,\quad\delta = -0.052\%\,,
\]
against the observed value $1.29333\,\mathrm{MeV}$.
This is \textbf{Prediction~\#105} of the BCT programme and the fourth
sub-$0.1\%$ result obtained in Phase~97.  Combined with Letter~29
(Predictions~\#102--104), this session delivers four simultaneous
sub-$0.1\%$ nuclear predictions --- kaon mass, proton mass, neutron mass, and
neutron--proton mass difference --- from a single NLO colour correction with
zero new free parameters.  The N-class coefficient $C_F = 4/3$ appears
identically in all four predictions, providing strong internal consistency for
the BCT NLO colour structure.
\end{minipage}
\end{center}
\vspace{10pt}
}]

%% ═══════════════════════════════════════════════════════════
\section{Introduction}
%% ═══════════════════════════════════════════════════════════

The neutron--proton mass difference $\Delta m_N = m_n - m_p = 1.29333\,\mathrm{MeV}$ is
one of the most cosmologically critical numbers in physics.  Were it negative,
the proton would be unstable; were it much larger than the electron mass, Big
Bang nucleosynthesis would produce almost no helium.  Its precise value
controls the $n/p$ freeze-out ratio and the primordial ${}^4$He abundance
$Y_p \approx 0.25$.  Deriving it from first principles is therefore a sharp
test of any fundamental theory.

The BCT programme has addressed $\Delta m_N$ in two previous phases.
Phase~48B~\cite{monograph} established the leading-order result
$\Delta m_N^{\rm LO} = \Lambda\alpha_0\pi/4 = 1.280\,\mathrm{MeV}$ ($-1.03\%$)
from the BCT SU(6) spin-flavour theorem.
Phase~81D~\cite{monograph} improved this to $1.285\,\mathrm{MeV}$
($-0.647\%$) by separating the strong NLO and electromagnetic Cottingham
contributions.  Both are sub-$1\%$ but not sub-$0.1\%$.

Letter~29~\cite{letter29} introduced the \textbf{BCT Colour Casimir Theorem}:
when meson modes in a hadronic decomposition carry their own NLO colour
corrections, the baryon NLO coefficient upgrades from $N = 3/4$ to
$C_F = (N_c^2-1)/(2N_c) = 4/3$, the SU(3) colour Casimir.  This theorem
produced Predictions~\#102--104: the kaon, proton, and neutron masses all
sub-$0.1\%$.

Here we apply the same theorem to the \emph{nucleon mass splitting} and obtain
Prediction~\#105.

%% ═══════════════════════════════════════════════════════════
\section{The BCT SU(6) Theorem at LO}
%% ═══════════════════════════════════════════════════════════

The proton (u,u,d) and neutron (u,d,d) differ by a single $u \leftrightarrow d$
quark exchange.  The BCT T$_d$ void lattice assigns $u$-type quarks to
octahedral voids (radius $r_{\rm oct}$) and $d$-type quarks to tetrahedral
voids (radius $r_{\rm tet}$).  The D$_{4h}$ tetragonal distortion of the BCT
lattice ($c/a = \sqrt{2}$) breaks $u$-$d$ isospin symmetry, generating the
quark mass difference~\cite{monograph}:
\begin{equation}
  \label{eq:mu_md}
  m_d - m_u = \Lambda\alpha_0\pi/2\,,
\end{equation}
with all quantities from the three BCT inputs
$\{r_{\rm oct},\,r_{\rm tet},\,\Lambda_{\rm QCD}\}$.

The BCT SU(6) spin-flavour overlap integral for the single-quark substitution
in the non-relativistic T$_d$ nucleon wave function gives
$F_{\rm SU(6)} = 1/2$~\cite{monograph}.  Physically, each nucleon contains three
quarks, but the T$_d$ doublet geometry of the $(u,d)$ pair suppresses the
single-quark matrix element by $1/2$ rather than the naive $1/3$.
The LO prediction is:
\begin{equation}
  \label{eq:dm_LO}
  \Delta m_N^{\rm LO} = (m_d - m_u)\cdot F_{\rm SU(6)}
  = \frac{\Lambda\alpha_0\pi}{4}
  = 1.280020\,\mathrm{MeV}\,,
\end{equation}
with observed $\Delta m_N = 1.29333\,\mathrm{MeV}$ and error $-1.03\%$.

%% ═══════════════════════════════════════════════════════════
\section{NLO Casimir Correction — Prediction \#105}
%% ═══════════════════════════════════════════════════════════

\textit{The Casimir upgrade.}\quad
The BCT Colour Casimir Theorem (Letter~29) states that when hadronic states
involve NLO colour corrections, the baryon self-energy coefficient upgrades to
the SU(3) Casimir $C_F$.  For the nucleon mass splitting, the relevant
correction is to the SU(6) factor $F_{\rm SU(6)}$: the single quark being
exchanged ($u \to d$) carries colour charge $C_F$ and acquires an NLO
colour-loop dressing.  The upgrade is:
\begin{equation}
  \label{eq:F_upgrade}
  F_{\rm SU(6)} = \frac{1}{2} \;\longrightarrow\;
  F_{\rm SU(6)}^{\rm NLO} = \frac{1}{2}(1 + C_F\alpha_0)\,,
\end{equation}
where $C_F = (N_c^2-1)/(2N_c) = 4/3$ and $N_c = 3$ is derived from the BCT
D$_4$ triality theorem~\cite{monograph}.

\textit{The NLO formula.}\quad
Substituting Eq.~(\ref{eq:F_upgrade}) into Eq.~(\ref{eq:dm_LO}):
\begin{equation}
  \label{eq:dm_NLO}
  \Delta m_N^{\rm NLO} = \frac{\Lambda\alpha_0\pi}{4}\,(1 + C_F\alpha_0)\,.
\end{equation}

\textit{Numerical evaluation.}\quad
With $\Lambda = 220\,\mathrm{MeV}$,
$\alpha_0 = r_{\rm oct}\,r_{\rm tet}/\pi = 0.00740806$,
$C_F = 4/3$:
\begin{align}
  \Lambda\alpha_0\pi/4 &= 1.280020\,\mathrm{MeV}, \label{eq:LO_num}\\
  C_F\alpha_0           &= \tfrac{4}{3}\times 0.00740806 = 0.00987741,\label{eq:CF_num}\\
  1 + C_F\alpha_0       &= 1.00987741, \label{eq:factor}
\end{align}
\begin{equation}
  \label{eq:result}
  \Delta m_N^{\rm NLO} = 1.292663\,\mathrm{MeV}\,,\quad
  \delta = -0.052\%\quad(\star\;\text{sub-}0.1\%)\,.
\end{equation}

against the CODATA value $\Delta m_N^{\rm obs} = 1.29333\,\mathrm{MeV}$.
This is \textbf{Prediction~\#105}.

%% ═══════════════════════════════════════════════════════════
\section{The N-Class Quartet}
%% ═══════════════════════════════════════════════════════════

The BCT Colour Casimir Theorem now governs four simultaneous predictions
in the nuclear sector, all from Phase~97:

\begin{table}[h]
\centering
\caption{Phase 97 nuclear sub-$0.1\%$ quartet.  All from
  $\{r_{\rm oct},\,r_{\rm tet},\,\Lambda_{\rm QCD}\}$; $C_F = 4/3$ throughout.}
\label{tab:quartet}
\small
\setlength{\tabcolsep}{4pt}
\begin{tabular}{llccc}
\toprule
Pred. & Observable & BCT Value & Obs. & Error \\
\midrule
\#102 & $m_K$ (NLO) & 493.534\,MeV & 493.677 & $-0.029\%$\,$\star$ \\
\#103 & $m_p$ (NLO) & 938.288\,MeV & 938.272 & $+0.002\%$\,$\star$ \\
\#104 & $m_n$ (NLO) & 939.541\,MeV & 939.565 & $-0.003\%$\,$\star$ \\
\#105 & $\Delta m_N$ & 1.2927\,MeV & 1.2933 & $-0.052\%$\,$\star$ \\
\bottomrule
\multicolumn{5}{l}{$\star$ Sub-0.1\%.  \quad All N-class: $N = C_F = 4/3$.}
\end{tabular}
\end{table}

The uniformity of the N-class coefficient $C_F = 4/3$ across all four
observables is a non-trivial internal consistency check.  In each case the
physical mechanism is the same: a quark undergoing an NLO colour-loop
interaction acquires a self-energy proportional to $C_F\alpha_0$, where $C_F$ is
the quadratic Casimir of the fundamental SU(3) representation.

\textit{Comparison with Phase~81D.}\quad
The Phase~81D result~\cite{monograph} obtained $\Delta m_N = 1.2846\,\mathrm{MeV}$
($-0.647\%$) by separating the contribution into a strong NLO term
$2m_\pi\alpha_0(1 + 3\alpha_0) = 2.045\,\mathrm{MeV}$ and an electromagnetic
Cottingham term $-0.76\,\mathrm{MeV}$ (taken from standard QCD+QED
calculations).  The present result
achieves better precision without invoking the Cottingham separation, using
instead the compact formula Eq.~(\ref{eq:dm_NLO}) which treats the full
$\Delta m_N$ holistically through the BCT geometric approach.

\textit{Cosmological note.}\quad
The BCT formula Eq.~(\ref{eq:dm_NLO}) evaluates to $\Delta m_N/m_N =
\alpha_0\pi C_F\alpha_0/4\ldots$, a tiny but precise fraction of the nucleon
mass set entirely by void geometry.  BCT naturally generates $\Delta m_N$
in the window $[m_e, 3\,\mathrm{MeV}]$ required for both proton stability and
Big Bang nucleosynthesis --- without any parameter tuning.

%% ═══════════════════════════════════════════════════════════
\section{Conclusion}
%% ═══════════════════════════════════════════════════════════

Applying the BCT Colour Casimir Theorem to the SU(6) spin-flavour factor
governing the neutron--proton mass difference gives:
\[
  \Delta m_N = \frac{\Lambda\alpha_0\pi}{4}(1+C_F\alpha_0)
             = 1.2927\,\mathrm{MeV}\,,\quad\delta=-0.052\%\,,
\]
from $\{r_{\rm oct},\,r_{\rm tet},\,\Lambda_{\rm QCD}\}$ alone, with no new
parameters.

Combined with Letter~29, Phase~97 delivers four simultaneous sub-$0.1\%$
predictions (\#102--\#105) for the four most fundamental nuclear observables
--- kaon mass, proton mass, neutron mass, and nucleon mass splitting --- all
governed by the single Casimir coefficient $C_F = (N_c^2-1)/(2N_c) = 4/3$
derived from BCT D$_4$ triality.

The BCT programme stands at \textbf{105 sub-$1\%$ predictions and 30
sub-$0.1\%$ predictions}, all from $\{r_{\rm oct},\,r_{\rm tet},\,\Lambda_{\rm QCD}\}$.

\bigskip
\noindent\textit{Data availability.}
All results reproduced from the formulas given; no datasets beyond
CODATA/PDG values cited are used.

\bigskip
\noindent$^\ast$ cabriem@gmail.com

\begin{thebibliography}{9}

\bibitem{monograph}
M.~R.\ Cabri\'e,
\textit{BCT Superfluid Lattice Model: Complete Derivation of Standard Model
Parameters},
Zenodo (2026), \href{https://doi.org/10.5281/zenodo.18884976}{doi:10.5281/zenodo.18884976}.

\bibitem{prl_letter}
M.~R.\ Cabri\'e,
\textit{Zero Free Parameters: Deriving 92 Standard Model Observables from
BCT Vacuum Geometry},
Zenodo (2026), \href{https://doi.org/10.5281/zenodo.18884415}{doi:10.5281/zenodo.18884415}.

\bibitem{letter29}
M.~R.\ Cabri\'e,
\textit{BCT Letter~29: The NLO Colour Correction to the Strange Sector ---
Three Sub-0.1\% Predictions},
Zenodo (2026), \href{https://doi.org/10.5281/zenodo.18884415}{doi:10.5281/zenodo.18884415}.

\bibitem{pdg2022}
R.~L.\ Workman \textit{et al.}\ (Particle Data Group),
Prog.\ Theor.\ Exp.\ Phys.\ \textbf{2022}, 083C01 (2022).

\end{thebibliography}

\end{document}
