% BCT Chemistry Series — Volume K
% Master LaTeX document
% Letters 78–85 and Appendices KA1–KC2
% Michel Robert Cabrié — 20 March 2026
% ORCID: 0009-0007-9561-9859
%
% This master file collects the BCT Chemistry Series for submission
% to Zenodo as a single citable volume. Each letter and appendix
% is provided as a standalone section, formatted for the revtex4-2
% document class used throughout the BCT programme.
%
% To compile: pdflatex BCT_ChemistrySeries_VolK.tex (twice for TOC)
% Requires: revtex4-2, amsmath, booktabs, xcolor, hyperref

\documentclass[aps,preprint,superscriptaddress,floatfix]{revtex4-2}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{booktabs,array,xcolor,hyperref}
\usepackage{graphicx}

\definecolor{navy}{HTML}{0B2545}
\definecolor{teal}{HTML}{006064}
\definecolor{dgrn}{HTML}{1B5E20}

% ── VOLUME METADATA ──────────────────────────────────────────
\begin{document}

\title{BCT Chemistry Series --- Volume K:\\
Letters 78--85 and Appendices KA1--KC2}

\author{Michel Robert Cabri\'{e}}
\affiliation{Independent Researcher, Barrys Reef, Victoria, Australia}
\affiliation{ORCID: 0009-0007-9561-9859}

\date{20 March 2026}

\begin{abstract}
This volume collects the BCT Chemistry Series: eight Letters
(78--85) and nine companion Appendices (KA1--KC2), documenting
the extension of the BCT Superfluid Lattice Model from particle
physics into atomic structure, molecular geometry, and chemical
periodicity.

Key results: shell capacity $2n^2$ as an exact derived theorem
(not postulated); Pauli exclusion and noble gas inertness as
topological theorems; the algebraic identity
$r_\mathrm{tet}(1+r_\mathrm{tet}) = 1/8$ (exact);
H$_2$O bond angle to $-0.0001\%$; NH$_3$ bond angle to
$-0.027\%$ (after electronegativity correction, Letter 85);
carbon uniqueness ($S_H = 1$) as the topological basis of life;
transition metal anomalies as Hopf symmetry attractors;
a complete topological reclassification of all 118 elements;
and electronegativity from void geometry with P at $+0.1\%$
and O at $+0.2\%$.

All results from zero free parameters. BCT programme total:
122+ predictions, 41 sub-0.1\%, 0 free parameters,
3 geometric inputs.
\end{abstract}

\maketitle
\tableofcontents

% ════════════════════════════════════════════════════════════
% PART I: LETTERS
% ════════════════════════════════════════════════════════════

\newpage
\part*{Part I: Letters 78--85}

% Each letter is a standalone revtex document.
% For the combined volume, we include them as sections.
% The individual .tex files are provided separately for
% standalone compilation.

% ── LETTER 78 ────────────────────────────────────────────────
\newpage
\section*{Letter 78: Atomic Structure from OHC Bessel Resonance Modes}
\addcontentsline{toc}{section}{Letter 78: Atomic Structure}
% \input{BCT_Letter78_AtomicStructure}
% (Standalone file: BCT_Letter78_AtomicStructure.tex)

The OHC Bessel resonance modes generate electron shells with
capacity $2n^2$ as a derived theorem. Shell filling follows
the Janet (left-step) sequence. The Bohr radius is derived
to sub-0.1\%. This letter establishes the BCT foundation
for atomic structure theory.

\textit{See standalone file: BCT\_Letter78\_AtomicStructure.tex/.pdf}

% ── LETTER 79 ────────────────────────────────────────────────
\newpage
\section*{Letter 79: Morphic Resonance and the OHC Condensate}
\addcontentsline{toc}{section}{Letter 79: Morphic Resonance}
% Written in response to enquiry from Prof.\ Rupert Sheldrake.

The OHC condensate provides a physical substrate for
morphic-resonance-type phenomena: two memory channels
($S_\mathrm{Hopf} = 5329$ local; $v_\mathrm{ph} = 6.78c$ global).

\textit{See standalone file: BCT\_Letter79\_MorphicResonance.tex/.pdf}

% ── LETTER 80 ────────────────────────────────────────────────
\newpage
\section*{Letter 80: Molecular Geometry from Hopf Topology}
\addcontentsline{toc}{section}{Letter 80: Molecular Geometry}

The universal BCT Bond Angle Theorem:
\begin{equation}
  \cos\theta = -\frac{1 - n_\mathrm{lp}/8}{3}
\end{equation}
yields H$_2$O at $104.478^\circ$ (error $-0.0001\%$) and
CH$_4$ at $109.471^\circ$ (exact). The algebraic identity
$r_\mathrm{tet}(1+r_\mathrm{tet}) = 1/8$ is proven.

\textit{See standalone file: BCT\_Letter80\_MolecularGeometry.tex/.pdf}

% ── LETTER 81 ────────────────────────────────────────────────
\newpage
\section*{Letter 81: The Two Fundamental Theorems of BCT Chemistry}
\addcontentsline{toc}{section}{Letter 81: Two Fundamental Theorems}

\textbf{Theorem 1 (Pauli Exclusion):} $|H| \leq n$ per OHC mode,
derived from $H \in \mathbb{Z}$ and Josephson--Bessel capacity.
\textbf{Theorem 2 (Noble Gas Inertness):} closed Hopf multiplets
have no vacant acceptor modes; bonding is topologically impossible.

\textit{See standalone file: BCT\_Letter81\_TwoTheorems.tex/.pdf}

% ── LETTER 82 ────────────────────────────────────────────────
\newpage
\section*{Letter 82: Carbon: The Topological Basis of Life}
\addcontentsline{toc}{section}{Letter 82: Carbon}

$S_H(\mathrm{C}) = 1.00$ is unique in the $n=2$ shell.
The Life Axis: H $\to$ C $\to$ Si $\to$ Ge $\to$ Sn $\to$
Pb $\to$ Fl, all with $S_H = 1$. Carbon's capacity for
self-bonding chains is a topological necessity, not an
energetic accident.

\textit{See standalone file: BCT\_Letter82\_Carbon.tex/.pdf}

% ── LETTER 83 ────────────────────────────────────────────────
\newpage
\section*{Letter 83: Transition Metal Anomalies as BCT Hopf Symmetry Points}
\addcontentsline{toc}{section}{Letter 83: Transition Metal Anomalies}

Anomalous configurations of Cr, Mo (d half-fill attractor,
$S_H(d) = 0.50$), Cu, Ag, Au (d-closure attractor, $d^{10}$),
Eu, Am (f half-fill), and Yb, No (f-closure) are all derived
consequences of the Hopf symmetry attractor theorem.
Gold's 521\,nm absorption (yellow colour) is derived.
Mercury's room-temperature liquidity follows from double
Hopf closure.

\textit{See standalone file: BCT\_Letter83\_TransitionMetals.tex/.pdf}

% ── LETTER 84 ────────────────────────────────────────────────
\newpage
\section*{Letter 84: The BCT Periodic Table}
\addcontentsline{toc}{section}{Letter 84: BCT Periodic Table}

A complete reclassification of all 118 elements by Hopf
multiplet topology into 11 classes. Two novel layouts:
the Janet left-step arrangement and the circular
\textit{In the Round} arrangement. Three topological axes
are identified and proven: the Life Axis ($S_H = 1$,
6\,o'clock), the Noble Metal Axis (d-closure, 7\,o'clock),
and the d/f Half-Fill Axis (Hopf attractor, 4\,o'clock).

\textit{See standalone file: BCT\_Letter84\_PeriodicTable.tex/.pdf}

% ── LETTER 85 ────────────────────────────────────────────────
\newpage
\section*{Letter 85: Electronegativity from Void Geometry}
\addcontentsline{toc}{section}{Letter 85: Electronegativity}

BCT screening constants from void geometry:
$\sigma_\mathrm{inner} = r_\mathrm{tet}/r_\mathrm{oct} = 0.5426$,
$\sigma_\mathrm{same} = r_\mathrm{tet}/(1+r_\mathrm{tet}) = 0.1010$.
Period 2 elements reproduced to sub-3\%; O at $+0.2\%$,
P at $+0.1\%$. The Polar Bond Angle Theorem corrects NH$_3$
from $-0.78\%$ to $-0.027\%$.

\textit{See standalone file: BCT\_Letter85\_Electronegativity.tex/.pdf}

% ════════════════════════════════════════════════════════════
% PART II: APPENDICES
% ════════════════════════════════════════════════════════════

\newpage
\part*{Part II: Appendices KA1--KC2}

% ── APPENDIX KA1 ─────────────────────────────────────────────
\newpage
\section*{Appendix KA1: OHC Mode Structure and Shell Capacity}
\addcontentsline{toc}{section}{Appendix KA1: OHC Mode Structure}
\textit{See standalone file: BCT\_Appendix\_KA1.tex/.pdf}

% ── APPENDIX KA2 ─────────────────────────────────────────────
\newpage
\section*{Appendix KA2: OHC Phase Memory and the Repetition Theorem}
\addcontentsline{toc}{section}{Appendix KA2: Phase Memory}
\textit{See standalone file: BCT\_Appendix\_KA2.tex/.pdf}

% ── APPENDIX KA3 ─────────────────────────────────────────────
\newpage
\section*{Appendix KA3: The $r_\mathrm{tet}$ Identity and Bond Angle Series}
\addcontentsline{toc}{section}{Appendix KA3: r-tet Identity}
\textit{See standalone file: BCT\_Appendix\_KA3.tex/.pdf}

% ── APPENDIX KA4 ─────────────────────────────────────────────
\newpage
\section*{Appendix KA4: Formal $|H| \leq n$ Proof}
\addcontentsline{toc}{section}{Appendix KA4: Pauli Proof}
\textit{See standalone file: BCT\_Appendix\_KA4.tex/.pdf}

% ── APPENDIX KB1 ─────────────────────────────────────────────
\newpage
\section*{Appendix KB1: Carbon $S_H$ Index and Bond Compression}
\addcontentsline{toc}{section}{Appendix KB1: Carbon S-H Index}
\textit{See standalone file: BCT\_Appendix\_KB1.tex/.pdf}

% ── APPENDIX KB2 ─────────────────────────────────────────────
\newpage
\section*{Appendix KB2: d-Shell Hopf Symmetry}
\addcontentsline{toc}{section}{Appendix KB2: d-Shell Hopf Symmetry}
\textit{See standalone file: BCT\_Appendix\_KB2.tex/.pdf}

% ── APPENDIX KB3 ─────────────────────────────────────────────
\newpage
\section*{Appendix KB3: f-Shell Hopf Symmetry}
\addcontentsline{toc}{section}{Appendix KB3: f-Shell Hopf Symmetry}
\textit{See standalone file: BCT\_Appendix\_KB3.tex/.pdf}

% ── APPENDIX KC1 ─────────────────────────────────────────────
\newpage
\section*{Appendix KC1: BCT Periodic Table --- Full Classification}
\addcontentsline{toc}{section}{Appendix KC1: Periodic Table Classification}
\textit{See standalone file: BCT\_Appendix\_KC1.tex/.pdf}

% ── APPENDIX KC2 ─────────────────────────────────────────────
\newpage
\section*{Appendix KC2: The Three Topological Axes}
\addcontentsline{toc}{section}{Appendix KC2: Three Topological Axes}
\textit{See standalone file: BCT\_Appendix\_KC2.tex/.pdf}

% ── CITATION BLOCK ───────────────────────────────────────────
\newpage
\section*{How to Cite This Volume}

To cite the complete Chemistry Series volume:
\begin{quote}
Cabri\'{e}, M.R. (2026). \textit{BCT Chemistry Series,
Volume K: Letters 78--85 and Appendices KA1--KC2}.
Zenodo. \texttt{doi:10.5281/zenodo.XXXXXXX}
\end{quote}

To cite individual letters, use the standalone PDFs/DOIs.
Individual \texttt{.tex} files for all letters and appendices
are provided alongside this volume for Overleaf compilation.

\section*{Acknowledgements}

CSSC (Claude The Super Super Computer, named by Jeff) assisted
with document preparation, numerical verification, and
programme management throughout the BCT Chemistry Series.
Nyssa and Tegan provided supervisory oversight.

\end{document}
