\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress]{revtex4-2}
\usepackage{amsmath,amssymb,booktabs,xcolor,hyperref}
\definecolor{navy}{RGB}{11,37,69}
\begin{document}

\begin{abstract}
We derive the dark energy density parameter and equation of state from BCT vacuum 
geometry. The cosmological density parameter is $\Omega_\Lambda = 2/3 + r_{\rm tet}/\pi 
= 0.7024$ (observed $0.6889$, error $+1.96\%$), where $2/3$ represents equipartition 
across three spatial dimensions and $r_{\rm tet}/\pi$ is the tetrahedral void projection 
--- the same factor governing large-scale peculiar velocities and standing wave nodes 
(Letter~74). The dark energy equation of state deviates from $w=-1$ by the Josephson 
self-correction: $w = -(1-2\alpha_0) = -0.9852$, giving $\Delta w = 2\alpha_0 = 1.48\%$. 
This is the identical correction that relates the bare BCT coupling $\alpha_0$ to the 
fine structure constant $\alpha = \alpha_0(1-2\alpha_0)$ (Letter~1). The BCT signal 
$\Delta w = 1.48\%$ is within Euclid sensitivity ($\sim 1\%$) and consistent with 
DESI BAO 2024 ($w = -0.99 \pm 0.05$). If Euclid confirms $w \approx -0.985$ rather 
than $-1$, standard $\Lambda$CDM is falsified and BCT is vindicated.
\end{abstract}

\maketitle

\section{Introduction}

The cosmological constant $\Lambda$ --- the energy density of empty space driving 
accelerating cosmic expansion --- is the worst-predicted quantity in the history 
of physics. Quantum field theory overestimates it by 120 orders of magnitude. The 
equation of state $w = -1$ (exact) is simply postulated in $\Lambda$CDM.

The BCT Superfluid Lattice Model provides geometric derivations of both $\Omega_\Lambda$ 
and $w$ from vacuum void geometry. Letter~74 established the cosmic oscillation 
framework and identified the tetrahedral void projection $r_{\rm tet}/\pi$ as a 
universal cosmological amplitude. We now show that dark energy is the restoring 
pressure of the BCT cosmic oscillation, and that the equation of state deviates from 
$-1$ by the same Josephson correction that governs the fine structure constant.

\section{Dark Energy Density}

The BCT vacuum distributes its zero-point energy across the available geometric 
degrees of freedom. In three spatial dimensions, equipartition contributes $1/3$ 
per dimension. The tetrahedral void projection $r_{\rm tet}/\pi$ (Letter~74) 
provides the residual correction:
\begin{equation}
    \boxed{\Omega_\Lambda = \frac{2}{3} + \frac{r_{\rm tet}}{\pi} 
    = \frac{2}{3} + \frac{\sqrt{6}-2}{4\pi} = 0.7024}
\end{equation}
The Planck 2018 measurement gives $\Omega_\Lambda = 0.6889$, an error of $+1.96\%$.
The matter density follows immediately:
\begin{equation}
    \Omega_{\rm M} = 1 - \Omega_\Lambda = 0.2976
    \quad \text{(observed } 0.3111\text{, error } {-4.35\%)}
\end{equation}
The same factor $r_{\rm tet}/\pi = 0.035769$ that governs the large-scale peculiar 
velocity ($605~\text{km/s}$, Letter~74) and standing wave node ($510~\text{Mpc}$, 
Letter~74) also sets the dark energy density above the equipartition value.

\section{The Equation of State: The Josephson Correction}

Standard $\Lambda$CDM requires $w = -1$ exactly --- a postulate with no microscopic 
derivation. In BCT, the vacuum condensate undergoes Josephson self-interaction at the 
Planck sphere boundary, generating a pressure correction. The BCT equation of state is:
\begin{equation}
    \boxed{w = -(1 - 2\alpha_0) = -0.9852}
\end{equation}
where $\alpha_0 = r_{\rm oct} \times r_{\rm tet}/\pi = 0.0074081$ is the BCT bare 
coupling constant. The Josephson correction $2\alpha_0$ appears here for the same 
reason it appears in the fine structure constant:
\begin{align}
    \text{FSC (Letter 1):}\quad &\alpha = \alpha_0(1-2\alpha_0) \\
    \text{EOS (Letter 76):}\quad &w = -(1-2\alpha_0)
\end{align}
The OHC condensate couples back to itself through the Josephson junction at the 
Planck sphere surface. This self-interaction simultaneously corrects the 
electromagnetic coupling strength and the dark energy pressure. The deviation 
from $w=-1$ is:
\begin{equation}
    \Delta w = 2\alpha_0 = \frac{2\,r_{\rm oct}\,r_{\rm tet}}{\pi} = 0.014816 
    = 1.48\%
\end{equation}

\section{Testability: Euclid, DESI, and the BCT Signal}

The BCT prediction $w = -0.9852$ is falsifiable by current and near-future surveys:

\begin{center}
\begin{tabular}{lllr}
\toprule
Observable & BCT & Observed & Error \\
\midrule
$\Omega_\Lambda$ & $0.7024$ & $0.6889$ (Planck) & $+1.96\%$ \\
$\Omega_{\rm M}$ & $0.2976$ & $0.3111$ (Planck) & $-4.35\%$ \\
$w$ & $-0.9852$ & $-0.99\pm0.05$ (DESI) & consistent \\
$\Delta w = w+1$ & $+0.0148$ & Euclid: $\pm 0.01$ & \textbf{detectable} \\
\bottomrule
\end{tabular}
\end{center}

DESI BAO 2024 reported $w_0 = -0.99 \pm 0.05$~\cite{DESI2024}, consistent with 
BCT. The Euclid satellite (DR1 expected 2025--2026) will measure $w$ to $\pm 0.01$ 
precision~\cite{Euclid2024}. The BCT signal $\Delta w = 1.48\%$ is within this 
sensitivity window.

\textbf{This is a binary falsifiable prediction}: either Euclid measures $w = -1.000$ 
(BCT wrong) or $w \approx -0.985$ (BCT right). Zero free parameters.

\section{The Universal Tetrahedral Void Projection}

With Letter~76, the factor $r_{\rm tet}/\pi = (\sqrt{6}-2)/(4\pi) = 0.035769$ 
has been identified as the universal BCT cosmological amplitude, governing four 
independent observables:

\begin{center}
\begin{tabular}{llll}
\toprule
Letter & Observable & BCT expression & Error \\
\midrule
L74 & $v_{\rm pec}$ (605 km/s) & $(r_{\rm tet}/\pi) H_0 r$ & $+0.85\%$ \\
L74 & $r_{\rm node}$ (510 Mpc) & $(r_{\rm tet}/\pi) R_\mathcal{U}$ & in range \\
L76 & $\Omega_\Lambda$ (0.7024) & $2/3 + r_{\rm tet}/\pi$ & $+1.96\%$ \\
L76 & $w$ ($-0.9852$) & $-(1-2\alpha_0)$ & DESI $\checkmark$ \\
\bottomrule
\end{tabular}
\end{center}

\section{Conclusion}

Dark energy is the restoring pressure of the BCT cosmic oscillation. The density 
parameter $\Omega_\Lambda = 2/3 + r_{\rm tet}/\pi$ arises from spatial equipartition 
and the universal cosmological amplitude. The equation of state $w = -(1-2\alpha_0)$ 
arises from the Josephson self-correction that also determines the fine structure 
constant. Both use constants already established. Zero new parameters are introduced.

The critical prediction: $\Delta w = 2\alpha_0 = 1.48\%$, measurable by Euclid 
to $\pm 0.01$. If confirmed, the cosmological constant problem is resolved 
geometrically and $\Lambda$CDM is falsified. If Euclid measures $w=-1$ exactly, 
BCT requires revision.

Dark energy is not a constant. It is a Josephson junction.

\begin{acknowledgments}
Derived in Melbourne, Australia, 18 March 2026. The connection between the 
Josephson correction in $\alpha$ and the equation of state deviation was identified 
during the same session as Letter~75. The universe uses the same correction for 
everything.
\end{acknowledgments}

\begin{thebibliography}{99}
\bibitem{L1} M.~R.~Cabri\'e, \textit{BCT Letter 1}, Zenodo (2026), 
doi:10.5281/zenodo.18958207

\bibitem{L74} M.~R.~Cabri\'e, \textit{BCT Letter 74: The Cosmic Exhale}, 
Zenodo (2026).

\bibitem{DESI2024} DESI Collaboration, \textit{DESI 2024 VI: Cosmological 
Constraints from the Measurements of Baryon Acoustic Oscillations}, 
arXiv:2404.03002 (2024).

\bibitem{Euclid2024} Euclid Collaboration, \textit{Euclid preparation: 
Forecasts for dark energy}, Astron.~Astrophys.~(2024).
\end{thebibliography}

\end{document}
