\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress]{revtex4-2}
\usepackage{amsmath,amssymb,booktabs,xcolor,hyperref}

\begin{document}

\begin{abstract}
We derive the arrow of time from BCT vacuum geometry through three nested 
mechanisms, all governed by the single constant $\alpha_0 = r_{\rm oct} \times 
r_{\rm tet}/\pi = 0.0074081$. At the Planck scale, Hopf charge quantisation 
$H \in \mathbb{Z}$ makes annihilation $H\to 0$ geometrically irreversible --- 
time is the count of irreversible OHC topological transitions. At the 
quantum-classical boundary, the measurement threshold $N_c = 1/\alpha_0 \approx 135$ 
(Letter~72) marks where geometric irreversibility becomes thermodynamic entropy 
increase. At the cosmological scale, the Josephson equation of state 
$w = -(1-2\alpha_0) \neq -1$ (Letter~76) breaks time-reversal symmetry: 
the expanding and contracting phases of the cosmic oscillation are not mirror 
images. The same $\alpha_0$ governing CP violation in baryogenesis (Letter~71) 
also governs T-violation in the cosmic equation of state. The arrow of time 
is a geometric theorem. The universe cannot run backwards because its equation 
of state does not permit it.
\end{abstract}

\maketitle

\section{Introduction}

The arrow of time is one of the deepest unsolved problems in physics. The 
fundamental equations --- Newton, Maxwell, Einstein, Schr\"{o}dinger, Dirac 
--- are all time-symmetric. Yet experience is overwhelmingly one-directional. 
The standard resolution appeals to the low-entropy initial condition of the 
universe without explaining why that condition obtained.

The BCT Superfluid Lattice Model provides a geometric derivation of temporal 
directionality through three nested mechanisms at the Planck, 
quantum-classical, and cosmological scales, all governed by $\alpha_0$.

\section{Mechanism I: Hopf Charge Irreversibility}

The OHC interior condensate supports topological excitations with integer 
Hopf charge $H \in \mathbb{Z}$ (Appendix~JH). When a Hopf defect annihilates 
$H = n \to 0$, integer topological charge is destroyed. This is geometrically 
irreversible: the pre-image of the Hopf map cannot be reconstructed from its 
annihilation products, because the winding number information is not conserved 
by any local operation.

\begin{definition}
The BCT time coordinate at any spacetime point is the cumulative count of 
irreversible Hopf transitions $H\to 0$ in its causal past:
\begin{equation}
    t_{\rm BCT} = \sum_{\rm past} \text{(irreversible OHC transitions)}
\end{equation}
\end{definition}

This coordinate is discrete, strictly monotonic, and one-directional. 
The Hopf transition rate is:
\begin{equation}
    \Gamma_{\rm BCT} = \alpha_0 \times H_0 = 1.62 \times 10^{-20}~\text{s}^{-1}
\end{equation}
corresponding to one irreversible topological event per $\sim 1950~\text{Gyr}$ 
per Hubble volume.

\section{Mechanism II: The Measurement Threshold}

Letter~72 established $N_c = 1/\alpha_0 \approx 135$ as the quantum-classical 
boundary --- when Josephson coupling to the OHC condensate reaches unity, 
wavefunction collapse is forced. In the context of the arrow of time, $N_c$ 
marks where Planck-scale geometric irreversibility becomes macroscopic 
thermodynamic entropy increase. This is the precise bridge between the quantum 
and thermodynamic arrows of time, at the exact scale $N_c = 1/\alpha_0$.

\section{Mechanism III: The Josephson Asymmetry}

Letter~76 derived $w = -(1-2\alpha_0) = -0.9852$. The deviation $\Delta w = 2\alpha_0$ 
from $w = -1$ has a fundamental consequence: the BCT cosmic oscillation is not 
time-reversal invariant.

A perfectly symmetric oscillator ($w = -1$) satisfies $t \to -t$ invariance: 
expansion is the exact time-reverse of contraction. The BCT oscillator does not: 
the Josephson correction $2\alpha_0$ explicitly breaks T-symmetry. The expanding 
and contracting universes are inequivalent.

By the CPT theorem, T-violation implies CP violation. In BCT, both arise from 
$\alpha_0$: the baryogenesis CP violation (Letter~71, governed by D4 triality) 
and the dark energy T-violation ($\Delta w = 2\alpha_0$, Letter~76) are two 
manifestations of the same geometric asymmetry.

\section{The BCT Arrow of Time Theorem}

\begin{theorem}[BCT Arrow of Time]
Time is strictly one-directional in the BCT universe because:
\begin{enumerate}
\item[(i)] $H \in \mathbb{Z}$ makes annihilation $H\to 0$ geometrically 
irreversible at the Planck scale.
\item[(ii)] $N_c = 1/\alpha_0$ translates Planck-scale irreversibility into 
macroscopic thermodynamic entropy increase.
\item[(iii)] $w = -(1-2\alpha_0) \neq -1$ breaks time-reversal symmetry at 
the cosmological scale.
\end{enumerate}
All three follow from $\alpha_0 = r_{\rm oct} \times r_{\rm tet}/\pi$.
\end{theorem}

\begin{center}
\begin{tabular}{llll}
\toprule
Scale & Mechanism & Role of $\alpha_0$ & Letter \\
\midrule
Planck & Hopf $H\to0$ & $\Gamma = \alpha_0 H_0$ & JH \\
Q$\to$C & Measurement & $N_c = 1/\alpha_0$ & L72 \\
Baryogenesis & CP violation & $J_{\rm BCT} = f(\alpha_0)$ & L71 \\
Cosmic & T-violation & $\Delta w = 2\alpha_0$ & L76 \\
\bottomrule
\end{tabular}
\end{center}

\section{The Cosmic Clock}

The BCT cosmic oscillation provides a universal clock $\theta = \omega_\mathcal{U} t$ 
currently at phase $60.4^\circ$. The time remaining to the first node is:
\begin{equation}
    t_{\rm node} = T_\mathcal{U}/2 - t_H = 43.1 - 14.45 = 28.65~\text{Gyr}
\end{equation}
At the node, Mechanism~III ensures the arrow does not reverse: $\Delta w = 2\alpha_0$ 
is phase-independent. Time flows forward through contraction as through expansion.

\section{Predictions}

\begin{enumerate}
\item $\Delta w = 2\alpha_0 = 1.48\%$ --- T-violation in dark energy, 
testable by Euclid ($\pm 0.01$).
\item Entropy production rate $\sim \alpha_0 H_0 = 1.62\times10^{-20}~\text{s}^{-1}$ 
per Hubble volume.
\item CP and T violation both $\propto \alpha_0$ --- testable at LHCb.
\item $\delta_{\rm CP} = -\pi/2$ (maximal) --- T2HK, DUNE, NOvA (Letter~38).
\end{enumerate}

\section{Conclusion}

The arrow of time is a geometric theorem. Time flows because $H \in \mathbb{Z}$ 
(irreversibility) and $w \neq -1$ (T-asymmetry). Both follow from 
$\alpha_0 = r_{\rm oct} \times r_{\rm tet}/\pi$. The universe cannot run 
backwards. Not because the initial condition was special. Because the geometry 
does not permit it.

\begin{acknowledgments}
Derived in Melbourne, Australia, 18 March 2026, in the same session as 
Letters 74--76. The question ``Why is time one-directional?'' was posed as an 
afterthought. The answer took approximately five minutes. The BCT 
choose-your-own-adventure continues.
\end{acknowledgments}

\begin{thebibliography}{99}
\bibitem{AppJH} M.~R.~Cabri\'e, \textit{Appendix JH}, Zenodo (2026),
doi:10.5281/zenodo.18975018
\bibitem{L71} M.~R.~Cabri\'e, \textit{BCT Letter 71: Baryogenesis}, Zenodo (2026).
\bibitem{L72} M.~R.~Cabri\'e, \textit{BCT Letter 72: Measurement Problem}, Zenodo (2026).
\bibitem{L74} M.~R.~Cabri\'e, \textit{BCT Letter 74: The Cosmic Exhale}, Zenodo (2026).
\bibitem{L76} M.~R.~Cabri\'e, \textit{BCT Letter 76: Dark Energy}, Zenodo (2026).
\end{thebibliography}

\end{document}
