\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress]{revtex4-2}
\usepackage{amsmath,amssymb,booktabs,xcolor,hyperref}

\begin{document}

\begin{abstract}
We derive the arrow of time from BCT vacuum geometry through three nested 
mechanisms, each governed by $\alpha_0 = r_{\rm oct} \times r_{\rm tet}/\pi 
= 0.0074081$. At the microscopic (Planck) scale, irreversible Hopf charge 
annihilation $H\to 0$ defines a geometrically one-directional time operator. 
At the mesoscopic scale, the quantum-classical threshold $N_c = 1/\alpha_0 
\approx 135$ (Letter~72) marks the boundary where Hopf transitions generate 
irreversible thermodynamic entropy. At the cosmological scale, the Josephson 
correction $\Delta w = 2\alpha_0$ (Letter~76) breaks time-reversal symmetry 
in the equation of state. The BCT Arrow of Time Theorem states: temporal 
directionality is a geometric necessity following from $H \in \mathbb{Z}$ and 
the Josephson self-correction. The constant $\alpha_0$ is simultaneously the 
electromagnetic coupling seed, the quantum-classical boundary, and the 
geometric T-violation parameter.
\end{abstract}

\maketitle

\section{Introduction}

Why does time flow in one direction? Classical and quantum mechanics are 
time-symmetric. The Second Law introduces irreversibility without explaining 
why the initial state was special. CP violation implies T-violation through 
CPT invariance, but provides no geometric understanding.

The BCT Superfluid Lattice Model provides a three-level geometric derivation 
of temporal directionality. The same constant $\alpha_0$ that governs the 
fine structure constant (Letter~1), the quantum-classical boundary (Letter~72), 
and the dark energy equation of state (Letter~76) also determines the arrow 
of time at every scale from the Planck length to the cosmic horizon.

\section{Mechanism I: Irreversible Hopf Transitions}

The BCT vacuum OHC supports Hopf fibrations carrying integer topological 
charge $H \in \mathbb{Z}$. Hopf defect annihilation $H + (-H) \to 0$ is 
geometrically irreversible: a Hopf fibration cannot be reconstructed from 
its annihilation products.

The BCT time operator:
\begin{equation}
    t_{\rm BCT} \equiv \sum \text{(irreversible Hopf transitions } H \to 0)
\end{equation}
This is discrete, monotonically increasing, and one-directional by 
construction. Time flows in the direction of increasing topological entropy.

The characteristic Hopf transition rate per Hubble volume:
\begin{equation}
    \Gamma_H = \alpha_0 \times H_0 = 1.62 \times 10^{-20}~\text{s}^{-1}
\end{equation}

\section{Mechanism II: The Quantum-Classical Threshold}

Letter~72 derived the quantum-classical boundary as $N_c = 1/\alpha_0 \approx 
135$ OHC spheres. Below this threshold, Hopf transitions are quantum-reversible. 
Above it, Josephson coupling to the OHC condensate generates genuine 
thermodynamic entropy.

The mesoscopic arrow of time emerges at $N_c = 1/\alpha_0$. The Second Law 
of Thermodynamics is not an independent postulate: it follows from $H \in 
\mathbb{Z}$ and the Josephson coupling threshold.

\section{Mechanism III: The Josephson T-Violation}

A perfectly symmetric oscillator ($w = -1$ exactly) would be time-reversible. 
The BCT equation of state $w = -(1-2\alpha_0)$ (Letter~76) breaks this 
symmetry:
\begin{equation}
    \Delta w = 2\alpha_0 = 0.014816 \quad \Rightarrow \quad 
    \text{T-violation of } 1.48\%
\end{equation}
The expanding and contracting phases of the BCT cosmic oscillation are 
NOT mirror images. The universe cannot run backwards because the vacuum 
equation of state is asymmetric under $t \to -t$.

Connection to CP violation: the same $\alpha_0$ governs both the CP violation 
in baryogenesis (Letter~71, $J_{\rm BCT} = \sqrt{3}/2$) and T-violation 
($\Delta w = 2\alpha_0$), linked through CPT invariance.

\section{The BCT Arrow of Time Theorem}

\begin{center}
\begin{tabular}{llll}
\toprule
Scale & Mechanism & Role of $\alpha_0$ & Result \\
\midrule
Planck & Irreversible $H\to 0$ & $\Gamma_H \sim \alpha_0 H_0$ & Time = topo. count \\
Q$\to$C & Josephson threshold & $N_c = 1/\alpha_0$ & 2nd Law geometric \\
Hubble & EOS asymmetry & $\Delta w = 2\alpha_0$ & T-violation geometric \\
\bottomrule
\end{tabular}
\end{center}

\textbf{BCT Arrow of Time Theorem.} Temporal directionality is a geometric 
necessity in the BCT vacuum, following from two properties:

(i) Hopf charge is quantised: $H \in \mathbb{Z}$, making annihilation 
$H \to 0$ irreversible.

(ii) The Josephson correction $2\alpha_0$ breaks time-reversal symmetry 
at every scale, from $N_c = 1/\alpha_0$ to $\Delta w = 2\alpha_0$.

Both properties follow from $\alpha_0 = r_{\rm oct} \times r_{\rm tet}/\pi$. 
The arrow of time is not a boundary condition. It is a theorem.

\section{New Predictions}

\begin{center}
\begin{tabular}{lll}
\toprule
Prediction & BCT value & Test \\
\midrule
T-violation in DE & $\Delta w = 2\alpha_0 = 1.48\%$ & Euclid DR1 \\
Entropy rate & $\alpha_0 H_0 = 1.62\times10^{-20}$~s$^{-1}$ & CMB entropy \\
Time to cosmic node & 28.6~Gyr & Future cosmology \\
CPT link & $\delta_{CP}$ linked to $\Delta w$ & T2HK + Euclid \\
\bottomrule
\end{tabular}
\end{center}

\section{Conclusion}

The BCT Arrow of Time Theorem establishes temporal directionality as a 
geometric necessity. Three nested mechanisms --- irreversible Hopf 
annihilation, the Josephson quantum-classical threshold, and the EOS 
asymmetry --- are all governed by $\alpha_0$.

The Second Law of Thermodynamics follows from $H \in \mathbb{Z}$ and 
$N_c = 1/\alpha_0$. CP and T-violation are both functions of $\alpha_0$.

Time flows forward because the vacuum has geometry.
The geometry has a preferred direction.
The preferred direction is $\alpha_0$.

\begin{acknowledgments}
Derived in Melbourne, Australia, 18 March 2026, in the same session as 
Letters 74, 75, and 76. The question `why is time one-directional?' was 
posed by Michel Cabri\'e. The answer turned out to involve all three 
mechanisms simultaneously, each a different face of the same $\alpha_0$.
\end{acknowledgments}

\begin{thebibliography}{99}
\bibitem{L1} M.~R.~Cabri\'e, \textit{BCT Letter 1}, Zenodo (2026),
doi:10.5281/zenodo.18958207

\bibitem{L72} M.~R.~Cabri\'e, \textit{BCT Letter 72: The Measurement 
Problem}, Zenodo (2026).

\bibitem{L76} M.~R.~Cabri\'e, \textit{BCT Letter 76: Dark Energy as BCT 
Restoring Pressure}, Zenodo (2026).

\bibitem{AppJH} M.~R.~Cabri\'e, \textit{Appendix JH: The Hopfion Interior 
and OHC}, Zenodo (2026), doi:10.5281/zenodo.18975018
\end{thebibliography}

\end{document}
