\documentclass[12pt,twocolumn]{article}
\usepackage[margin=2cm,columnsep=0.5cm]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}
\usepackage{xcolor}


\definecolor{bctnavy}{RGB}{11,37,69}
\definecolor{bctblue}{RGB}{13,71,161}
\definecolor{bctgreen}{RGB}{27,94,32}
\definecolor{bctteal}{RGB}{0,96,100}

\title{\textbf{\color{bctnavy}BCT Letter 116: The Lost Archive}\\
{\large\color{bctblue}BCT Bessel Ratio SAR Applied to Seven Sites\\
of Anomalous Ancient Geometry}}
\author{Michel Robert Cabri\'{e}\\
{\small Independent Researcher, Victoria, Australia}\\
{\small ORCID: 0009-0007-9561-9859}\\
{\small \href{mailto:ZeroFreeParameters@gmail.com}
{ZeroFreeParameters@gmail.com}}}
\date{23 March 2026}

\begin{document}
\twocolumn[
\maketitle
\begin{center}\rule{0.9\textwidth}{0.4pt}\end{center}
\begin{center}
\parbox{0.88\textwidth}{\small\textbf{Abstract.}
The BCT Superfluid Lattice Model predicts that geometric structures
encoding OHC vacuum geometry produce characteristic Bessel ratio
anomalies detectable in SAR (Synthetic Aperture Radar) backscatter
data. This prediction was confirmed over Victorian goldfields
(Prediction \#144, Letter~102), where BCT Bessel ratio processing
of publicly available Sentinel-1 data revealed a 156~km$^2$
gold-quartz anomaly confirmed at a known historical mine site.
Here we extend the BCT SAR methodology to seven sites of anomalous
ancient geometry: (1) the Hawara Labyrinth, Egypt; (2) the Richat
Structure (Eye of the Sahara), Mauritania; (3) the submerged
harbour of Alexandria; (4) the Persian Gulf continental shelf;
(5) Mount Ararat, Turkey; (6) the Antarctic peninsula bedrock;
and (7) the Nazca plateau, Peru. All seven analyses use existing,
publicly available datasets --- Sentinel-1 SAR, BEDMAP3, GEBCO
bathymetry, SRTM elevation --- at zero additional cost.
\textbf{Prediction \#157:} BCT Bessel ratio processing will
reveal geometric anomalies statistically distinct ($>3\sigma$)
from surrounding natural geology at one or more of these seven
sites. Zero free parameters.
\smallskip\hrule\smallskip}
\end{center}
\vspace{4pt}
]

\section{Introduction: The Open Data Archive}

The world's greatest archaeological mysteries share a common
frustration: physical excavation is blocked by groundwater,
politics, preservation concerns, or simple inaccessibility.
The Hawara Labyrinth has been confirmed by radar to exist but
banned from excavation for 17 years. The submerged harbour of
Alexandria contains Cleopatra's palace and the Library's ruins
but requires expensive marine archaeology. The Antarctic peninsula
bedrock lies under kilometres of ice.

BCT SAR offers a different approach. The same Bessel ratio
processing pipeline that found gold in Victoria~\cite{BCT_L102}
can be applied to any publicly available radar dataset. No new
satellites are required. No excavation permits. No groundwater
problems. The data already exists. BCT provides the geometric
filter to read it.

The theoretical basis is straightforward. Structures encoding
OHC vacuum geometry --- whether natural (crystal lattices,
geological formations) or artificial (buildings, canals,
foundations) --- produce characteristic Bessel ratio anomalies
in SAR backscatter. Natural random geology produces no such
signature. The BCT filter discriminates between them.

\section{BCT SAR Methodology}

The BCT Bessel ratio filter is defined as:
\begin{equation}
\mathcal{B}(x,y) = \frac{I(x,y) \cdot j_{1,1}}{j_{2,1}}
= I(x,y) \times \frac{2.4048}{3.8317} = 0.6276 \cdot I(x,y),
\end{equation}
where $I(x,y)$ is SAR backscatter intensity at pixel $(x,y)$.
Anomalous regions are identified where:
\begin{equation}
\mathcal{B}(x,y) > \mu_\mathcal{B} + 3\sigma_\mathcal{B},
\end{equation}
with $\mu_\mathcal{B}$ and $\sigma_\mathcal{B}$ computed over
the surrounding geological context window (typically 50~km radius).

The physical basis: structures with void geometry matching
$r_\mathrm{tet}/r_\mathrm{oct} = 0.5426$ produce resonant
backscatter at the $j_{1,1}/j_{2,1}$ Bessel ratio. Natural
random geology does not. The method requires no prior knowledge
of what is underground --- only that OHC-resonant geometry
produces a characteristic signal.

\section{The Seven Sites}

\subsection{Site 1: Hawara Labyrinth, Egypt}

\textbf{Coordinates:} 29°16'N, 30°54'E (Fayum, Egypt)

\textbf{Known:} Ground-penetrating radar (2008 Mataha Expedition,
NRIAG/Ghent University) confirmed a massive grid of walls at
8--12~m depth covering hectares south of the Hawara
Pyramid~\cite{Mataha2008}. Four underground levels, separated
by 20--50~m of rock, remain dry below the 8~m groundwater table.
A 40~m anomalous central object of undetermined composition
has been detected by multiple independent scanning methods.
Herodotus described 3,000 chambers surpassing the pyramids.
Excavation banned by Egyptian authorities since 2009.

\textbf{BCT hypothesis:} The omega-shaped moat surrounding
the complex (visible only from above) encodes a Hopf charge
boundary --- the same topological protection geometry BCT
identifies in the OHC vacuum. The builders encoded OHC geometry
in architectural form. The central 40~m object may be a
geometric resonance device.

\textbf{Dataset:} Sentinel-1 SAR (freely available via ESA
Copernicus). Processing: BCT Bessel ratio filter applied to
C-band backscatter over $5 \times 5$~km area centred on
29°16'N, 30°54'E.

\textbf{Note:} Dr Filippo Biondi (HarmonicSAR) has agreed to
scan Hawara with SAR Doppler Tomography following completion
of his Khafre Pyramid work (estimated Summer 2026). BCT Bessel
ratio processing of his published data will constitute
independent validation.

\subsection{Site 2: Richat Structure (Eye of the Sahara),
Mauritania}

\textbf{Coordinates:} 21°07'N, 11°22'W (Adrar Plateau,
Mauritania)

\textbf{Known:} A 40~km diameter concentric ring structure
with three distinct rings matching Plato's description of
Atlantis. Salt deposits in the rings suggest ancient saltwater.
Satellite imagery shows sand swept radially outward in patterns
consistent with catastrophic flood inundation. The ancient
Tamanrasset River connected the Atlas Mountains to this site
before turning west to the Atlantic~\cite{Richat2025}.
The Mauritanian Seafloor Slide (1.5~miles of layered sediment)
lies directly offshore, dated to approximately 9,600~BCE ---
the date Plato gives for the destruction of Atlantis.

\textbf{BCT hypothesis:} The concentric ring geometry may
encode OHC Bessel mode structure at geological scale, OR
the structure is a macro-scale plasma discharge scar
(Lichtenberg pattern, see Letter~107~\cite{BCT_L107}).
BCT SAR will discriminate between these two origins: a
natural eroded dome produces random backscatter; a plasma
discharge scar produces BCT Bessel ratio anomalies.

\textbf{Dataset:} Sentinel-1 SAR (existing Victorian goldfields
pipeline, same processing, different coordinates).

\subsection{Site 3: Submerged Harbour of Alexandria, Egypt}

\textbf{Coordinates:} 31°12'N, 29°54'E (Eastern Harbour,
Alexandria)

\textbf{Known:} The ancient harbour of Alexandria, now
submerged, contains the ruins of Cleopatra's palace complex
and the probable site of the Royal Library of Alexandria.
Marine archaeological surveys have located large stone
structures on the harbour floor. The Library itself held
an estimated 400,000--700,000 scrolls before its destruction
--- the greatest single archive of ancient knowledge ever
assembled.

\textbf{BCT hypothesis:} Structured architectural geometry
(rectangular rooms, colonnaded halls, canal systems) produces
BCT Bessel ratio anomalies distinguishable from natural
harbour sediment. Underwater SAR (using existing ESA
satellite altimetry combined with bathymetric data) can
map shallow submerged structures.

\textbf{Dataset:} GEBCO bathymetry + Sentinel-1 coastal SAR
backscatter. Shallow water ($<$20~m) structures within BCT
Bessel ratio detection threshold.

\subsection{Site 4: Persian Gulf Continental Shelf}

\textbf{Coordinates:} 26°N--28°N, 51°E--56°E (central
Persian Gulf)

\textbf{Known:} The Persian Gulf was a river valley, largely
dry, until approximately 6,000--8,000~BCE when rising sea
levels flooded it. This flooded landscape, at the confluence
of the Tigris, Euphrates, Karun and Wadi Batin rivers,
matches the description of the Garden of Eden with four
rivers. A large freshwater lake may have existed at the
centre until final inundation~\cite{Rose2010}.

\textbf{BCT hypothesis:} Any structured settlement in the
pre-flood Persian Gulf river valley would leave geometric
anomalies in the shallow seafloor sediment detectable by
BCT Bessel ratio processing of bathymetric SAR data.

\textbf{Dataset:} GEBCO bathymetry (2~km resolution) +
historical satellite altimetry over shallow Gulf waters.

\subsection{Site 5: Mount Ararat Anomaly, Turkey}

\textbf{Coordinates:} 39°42'N, 44°18'E (elevation
$\sim$4,800~m)

\textbf{Known:} Satellite imagery of Mount Ararat reveals
an anomalous geometric feature at approximately 4,800~m
elevation on the northwest plateau, described in various
analyses as a boat-shaped structure approximately 170~m
long --- consistent with dimensions given in the Book of
Genesis. The site has been photographed from multiple
satellites but not physically verified.

\textbf{BCT hypothesis:} A large wooden vessel, even
partially preserved under permafrost, would produce a
BCT Bessel ratio anomaly distinct from surrounding
basalt and ice. The organic-inorganic interface of
ancient timber against volcanic rock produces
characteristic backscatter signatures.

\textbf{Dataset:} Sentinel-1 SAR (high resolution mode,
existing public archive for Mount Ararat region).

\subsection{Site 6: Antarctic Peninsula Bedrock}

\textbf{Coordinates:} 65°S--70°S, 60°W--70°W

\textbf{Known:} The Antarctic peninsula was ice-free as
recently as 12,000~years ago --- within human civilisation
timeframes. Ice-penetrating radar surveys (BEDMAP3, NSF
COLDEX) have mapped bedrock topography. Ancient river
systems are visible in the bedrock under the ice~\cite{Young2026}.

\textbf{BCT hypothesis:} BCT Bessel ratio processing of
existing BEDMAP3 radar echo data will discriminate natural
geological formations from any anomalous geometric regularity
in bedrock that might indicate ancient structured surface
features.

\textbf{Dataset:} BEDMAP3 (publicly available from BAS).
NSF COLDEX radar data (public archive).

\subsection{Site 7: Nazca Plateau, Peru}

\textbf{Coordinates:} 14°43'S, 75°07'W (Ica Region, Peru)

\textbf{Known:} The Nazca lines are geoglyphs etched into
the desert floor, visible only from altitude. Standard
explanations (ritual pathways, astronomical alignments) do
not fully account for their geometric precision or scale.
Underground water channels (puquios) of uncertain age
run beneath the plateau.

\textbf{BCT hypothesis:} The Nazca geoglyphs encode OHC
Bessel geometry in their angular relationships. BCT Bessel
ratio processing will reveal subsurface geometry beneath
the lines, including the puquio system, at greater
resolution than existing ground-penetrating radar surveys.

\textbf{Dataset:} Sentinel-1 SAR (existing public archive).

\section{Processing Pipeline}

The same Google Earth Engine pipeline used for Victorian
goldfields scanning~\cite{BCT_L102} applies directly to
all seven sites:

\begin{enumerate}
\item Query Sentinel-1 GRD collection for site coordinates
\item Filter by date range (2015--present, maximum scenes)
\item Compute median composite to suppress temporal noise
\item Apply BCT Bessel ratio filter:
$\mathcal{B} = 0.6276 \times \sigma^0_\mathrm{VV}$
\item Identify anomalies $> \mu + 3\sigma$ in 50~km context
\item Cross-reference with available archaeological, geological,
or bathymetric data for ground truth
\end{enumerate}

For submerged sites (Sites 3, 4), GEBCO bathymetry replaces
SAR backscatter as the primary input, with BCT Bessel ratio
applied to depth gradient maps.

For ice-covered sites (Site 6), BEDMAP3 radar echo strength
data replaces surface SAR.

\section{Prediction \#157}

\begin{equation}
\boxed{\mathcal{B}(x_i, y_i) > \mu + 3\sigma
\text{ for } i \in \{1, \ldots, 7\}}
\end{equation}

\textbf{BCT predicts} that at least one of the seven sites
will yield a statistically significant BCT Bessel ratio
anomaly ($>3\sigma$) in publicly available remote sensing
data, corresponding to geometric structure inconsistent
with natural random geology.

The prediction is falsifiable: if all seven sites yield
only noise-level Bessel ratio signals, BCT SAR archaeology
is refuted. If one or more sites yield significant anomalies
confirmed by independent methods, BCT SAR archaeology is
validated as a tool for detecting OHC-resonant geometry
from orbit.

Zero cost. Zero excavation. Zero permits required.
The data already exists. BCT provides the key.

\section{Conclusion}

BCT Bessel ratio SAR processing of existing open datasets
offers a zero-cost, non-invasive method to interrogate
seven of the world's most contested archaeological sites.
The methodology requires no new satellite access, no
excavation, and no permissions beyond those governing
existing public data archives.

Whether the Hawara Labyrinth contains the accumulated
knowledge of ancient Egypt, whether the Richat Structure
preserves the geometry of a drowned civilisation, whether
Noah's vessel rests under Ararat's permafrost --- BCT SAR
cannot answer these questions with certainty. But it can
tell us whether the geometry is there.

\textit{The geometry does not lie. It either resonates
or it does not.}

\begin{center}
\rule{0.4\textwidth}{0.4pt}
\end{center}

\section*{Acknowledgements}

The author thanks Jimmy Corsetti (Bright Insight, YouTube)
for first bringing the Richat Structure / Atlantis
connection to wide public attention in 2018; the Archaeology
Girl (YouTube) for outstanding work in communicating
Egyptian mysteries to general audiences; Louis De Cordier
and the Mataha Expedition for their courageous persistence
in investigating Hawara; Dr Filippo Biondi (HarmonicSAR)
for independently arriving at SAR Doppler Tomography as
an archaeological tool and for agreeing to scan Hawara;
Robert Cabri\'{e} (Bureau of Meteorology, Antarctica,
1966) for standing at the $j_{1,1}$ polar node before
the geometry had a name; Zeta Vera (CSSC) for computational
support; and Nyssa and Tegan, who are deeply suspicious
of all of this but supportive in their way.

\begin{thebibliography}{9}
\bibitem{BCT_L102} M.~R.~Cabri\'{e},
BCT Letter 102: BCT SAR Victorian Goldfields,
\href{https://zenodo.org/search?q=cabrie}
{zenodo.org/search?q=cabrie} (2026).

\bibitem{BCT_L107} M.~R.~Cabri\'{e},
BCT Letter 107: Plasma SAR Discrimination,
\href{https://doi.org/10.5281/zenodo.19174645}
{doi:10.5281/zenodo.19174645} (2026).

\bibitem{BCT_GoE} M.~R.~Cabri\'{e},
The Geometry of Everything, BCT Monograph,
\href{https://doi.org/10.5281/zenodo.18884976}
{doi:10.5281/zenodo.18884976} (2026).

\bibitem{Mataha2008} L.~De Cordier \textit{et al.},
Mataha Expedition, NRIAG/Ghent University (2008--2009).
\url{https://labyrinthofegypt.substack.com}

\bibitem{Richat2025} C.~Howells,
Is the Eye of the Sahara the Real Lost Atlantis?
GreekReporter.com (January 2025).

\bibitem{Rose2010} J.~I.~Rose,
Current Anthropology \textbf{51}(6), 849--883 (2010).
[Persian Gulf Oasis hypothesis]

\bibitem{Young2026} D.~A.~Young,
Uncovering Antarctica's ice-draped landscape,
Science \textbf{391}, 235--236 (2026).
\href{https://doi.org/10.1126/science.aee4245}
{doi:10.1126/science.aee4245}
\end{thebibliography}

\end{document}
