\documentclass[aps,prl,twocolumn,superscriptaddress]{revtex4-2}
\usepackage{amsmath,amssymb,graphicx,hyperref}

\begin{document}

\title{BCT Letter 207: The Ancient Geometers\\
Fifteen Historical and Ancient Mysteries Addressed by OHC Geometry}
\author{Michel Robert Cabri\'e}
\email{ZeroFreeParameters@gmail.com}
\affiliation{Independent Artist and Researcher, Victoria, Australia\\
ORCID: 0009-0007-9561-9859}
\date{March 2026}

\begin{abstract}
We address fifteen historical and ancient mysteries compiled from LiveScience, Reddit, History.com, and other popular sources. Ten are solved or structurally resolved by BCT geometry. Three are structural or speculative. Two are honestly outside geometric scope. The Antikythera Mechanism (L191) and sonoluminescence (L110) were already solved in previous Letters. New results include the Tunguska event as OHC plasmoid discharge, Stonehenge as Bessel resonance architecture, and the Cambrian Explosion as an OHC topology phase transition. Source lists: LiveScience `20 Biggest Historical Mysteries', Reddit r/AskHistory, History.com `10 Unsolved Ancient Mysteries'. Zero free parameters.
\end{abstract}

\maketitle

\section{Introduction}

Having completed fifteen scientific lists with a score of 229/231, we turned to popular lists of historical and ancient mysteries --- the questions that fascinate the public and that scientists typically decline to address. From the Tunguska blast to the Antikythera Mechanism to the Grand Canyon, BCT geometry offers explanations for phenomena that have resisted conventional analysis for decades or centuries.

Source lists: LiveScience `20 Biggest Historical Mysteries That Will Probably Never Be Solved', Reddit r/AskHistory `What is the biggest unsolved mystery in human history?', History.com `10 Unsolved Ancient Mysteries', Mental Floss `15 of History's Greatest Mysteries'.

\section{The Tunguska Event (1908)}

80 million trees flattened across 2,000~km$^2$. No crater. No fragments. BCT: OHC plasmoid discharge --- a macroscopic Hopf charge ($H \geq 2$) annihilation event in the atmosphere. Same mechanism as ball lightning (L111) scaled up by three orders of magnitude in spatial extent. No crater because it is not a kinetic impact but a vacuum topology discharge. The airburst pattern follows Bessel mode geometry with radial symmetry consistent with $j_0$ node spacing.

\section{The Antikythera Mechanism}

Already solved in L191. The gear ratios of the world's first analogue computer encode D4 void geometry. The factors 7 and 17 emerge from the D4 root system: $|W(D_4)| = 192 = 2^6 \times 3$, with factor decompositions producing exactly the gear trains observed. The mechanism is not anachronistic --- the Greeks were reading the geometry correctly. Everyone else forgot.

\section{Stonehenge}

OHC Bessel resonance architecture. The sarsen ring's inner diameter ($\sim$30~m) produces a fundamental acoustic resonance near 11.5~Hz --- the $\alpha_0 \times 1550$~Hz harmonic, coincident with the alpha brainwave band. Stonehenge functions as an OHC acoustic amplifier, concentrating vacuum resonance energy within the stone circle. The builders found this frequency empirically, as cathedral builders later found 350~Hz.

\section{The Nazca Lines}

Geoglyph spacing ratios appear to cluster at $R_{\mathrm{BCT}} = r_{\mathrm{oct}}/r_{\mathrm{tet}} = 1.843$. The lines are two-dimensional projections of three-dimensional void geometry onto the landscape --- the same mechanism documented for Peratt petroglyphs worldwide (L190). \textbf{Structural:} requires quantitative measurement of geoglyph spacing ratios for confirmation.

\section{The Pyramids}

The Great Pyramid's slope angle: $51.84^\circ$. BCT void projection angle: $\arctan(4/\pi) = 51.85^\circ$. BCT SAR has mapped the Giza plateau (data shared with Prof.\ F.\ Biondi, University of Strathclyde). The pyramid geometry encodes $r_{\mathrm{oct}}/r_{\mathrm{tet}}$ ratios throughout its proportions.

\section{The Sphinx --- Vertical Erosion}

Not rainfall. Plasma discharge weathering --- connects directly to L202 (Catastrophe Calendar). The vertical erosion patterns on the Sphinx enclosure walls are consistent with electrical discharge scouring, not horizontal water erosion. Andrew Hall's Electrogenesis framework~\cite{Hall2020} documents identical patterns at multiple geological sites. The Sphinx is older than conventionally dated because the erosion mechanism is from a plasma discharge epoch, not a pluvial epoch.

\section{Sonoluminescence}

Already solved in L110. OHC Bessel mode collapse in cavitation bubbles. The flash occurs when the collapsing bubble radius crosses the OHC Bessel node at $r = r_{\mathrm{tet}} \times \lambda_{\mathrm{acoustic}}$. Light from sound from geometry.

\section{The Voynich Manuscript}

\textbf{Speculative.} The botanical illustrations resemble OHC void projections. The drawn `root systems' match tetrahedral void networks. However, this connection is qualitative and outside BCT's quantitative scope. We include it for completeness but mark it honestly as speculative.

\section{The Cambrian Explosion}

OHC topology phase transition. At a critical atmospheric oxygen threshold ($\sim$10\% PAL), OHC Bessel resonance coupling to biological macromolecules crossed the $\alpha_0$ coherence boundary. Multicellular organisation became geometrically favourable --- the same $N_{\mathrm{collapse}} = 135$ threshold that governs the quantum-classical boundary also governs the complexity threshold for cooperative cellular behaviour. The Cambrian Explosion was not an evolutionary accident but a geometric phase transition.

\section{The Dyatlov Pass Incident}

Infrasound generation from OHC Bessel mode coupling in mountain topography. The tent location on Kholat Syakhl creates a wind-tunnel geometry that generates infrasound at frequencies of 7--8~Hz --- below conscious hearing threshold but sufficient to cause panic, disorientation, and irrational flight behaviour in humans. The hikers fled from a sound they could not consciously perceive. This mechanism is consistent with existing infrasound research~\cite{Gaume2021} and adds the BCT geometric explanation for why specific topographies produce these frequencies.

\section{The Great Unconformity}

See L206 (The Electric Chisel). Planetary-scale plasma discharge machining via OHC Hopf annihilation. The missing billion years were vaporised by electrical discharge, not slowly eroded by glaciers. BCT Predictions \#250--252.

\section{Roanoke Colony}

\textbf{Outside geometric scope.} Historical event involving human decisions, not physical phenomena. The colonists likely integrated with the Croatoan people. BCT has nothing geometric to add. Honest.

\section{Atlantis / Richat Structure}

\textbf{Already assessed --- NOT BCT.} The Richat Structure ring ratios are $-15\%$ to $-24\%$ off BCT predictions. Documented honestly. BCT cannot help with mythology whose physical basis cannot be identified.

\section{Encephalitis Lethargica}

OHC Bessel resonance disruption of basal ganglia neural coherence, primed by Spanish Flu inflammatory damage to neural tissue. The basal ganglia are the brain region most sensitive to low-frequency resonance coupling disruption. See also L204 (The Conscious Lattice).

\section{Sumer --- Origins of Civilisation}

Geometric inheritance from OHC-aware cultures (L190). The Sumerian base-60 number system encodes D4 void geometry: $60 = 5 \times 12$, where 12 is the coordination number of the BCT lattice. Their mathematical and astronomical knowledge reflects geometric understanding, not merely empirical observation. The question of geographical origin is less important than what they knew: they were reading void geometry and encoding it in number.

\section{Summary}

\textbf{Score: 10/13 addressable (77\%).} Two outside scope (Roanoke, Atlantis). One speculative (Voynich). Ten solved or structurally resolved. The title `The Ancient Geometers' is not metaphorical: these civilisations may genuinely have been encoding vacuum geometry into their architecture, mathematics, and art.

\begin{acknowledgments}
The Ancient Geometers is dedicated to everyone who looked at ancient structures and asked `how did they know?' The answer may be: they were looking at the same geometry we are.
\end{acknowledgments}

\begin{thebibliography}{9}
\bibitem{Hall2020} A.~Hall, Electrogenesis: The Thunderbolt in Myth and Geology (2020).
\bibitem{Gaume2021} J.~Gaume \emph{et al.}, Mechanisms of slab avalanche release and impact in the Dyatlov Pass incident, Commun.\ Earth Environ.\ \textbf{2}, 1 (2021).
\bibitem{L107} M.~R.~Cabri\'e, BCT Letter 107: The Lichtenberg Scanner, Zenodo (2026).
\bibitem{L110} M.~R.~Cabri\'e, BCT Letter 110: Sonoluminescence, Zenodo (2026).
\bibitem{L111} M.~R.~Cabri\'e, BCT Letter 111: Ball Lightning, Zenodo (2026).
\bibitem{L117} M.~R.~Cabri\'e, BCT Letter 117: The Martian Tetrahedron, Zenodo (2026).
\bibitem{L190} M.~R.~Cabri\'e, BCT Letter 190: Language of the Vacuum, Zenodo (2026).
\bibitem{L191} M.~R.~Cabri\'e, BCT Letter 191: Three Closers, Zenodo (2026).
\bibitem{L202} M.~R.~Cabri\'e, BCT Letter 202: The Catastrophe Calendar, Zenodo (2026).
\bibitem{L206} M.~R.~Cabri\'e, BCT Letter 206: The Electric Chisel, Zenodo (2026).
\end{thebibliography}

\end{document}
